\section{Sphinx Packet Format}
\label{sec:sphinx}

HOPR uses the Sphinx packet format \cite{sphinxpaper} to encapsulate and route data packets in order to ensure sender and recipient unlinkability. The Sphinx packet format determines how mixnet packets are created and transformed before relaying them to the next downstream node in a way that does not leak path information to relayers or other parties. Each Sphinx packet consists of two parts, a header and an onion-encrypted payload:

\begin{figure}[H]
    \centering
    \begin{tikzpicture}
        \draw (0,0) rectangle (10,0.5);
        \draw (0,-0.5) rectangle (10,0);
        \draw (0,-1) rectangle (10,-0.5);

        \draw (5,0.25) node {key derivation $\alpha$};
        \draw (5,-0.25) node {blinded routing information $\beta$};
        \draw (5,-0.75) node {integrity tag $\gamma$};

        \draw[decoration={brace,raise=5pt,mirror},decorate] (0,0.5) -- node[left=8pt] {Header} (0,-1);

        \draw (0,-2.25) rectangle (10, -1.25);
        \draw (5,-1.75) node {padded and onion-encrypted payload  $\delta$};

        \draw[decoration={brace,raise=5pt,mirror},decorate] (0,-1.25) -- node[left=8pt] {Body} (0,-2.25);
    \end{tikzpicture}
    \label{fig:sphinxoverview}
    \caption{Schematic overview of a SPHINX packet}
\end{figure}

\subsection{Construction}

The following explains how a Sphinx packet is created and how it is transformed at each hop before arriving at its final destination. At first, the sender chooses a path (see Section \ref{sec:path-selection}), and derives shared keys with each node on the path. The shared keys serve as a master secret to derive subkeys. These subkeys are used to blind the routing information in such a way that nodes can solely determine the next downstream node, and also to create an authentication tag to check the integrity of the header. In addition, the sender applies one layer of encryption for each node along the chosen path to the payload. This accomplished, the sender finally sends the packet to the first hop.

Once a node receives a mixnet packet, it first derives the key that it has shared with the sender of the packet and checks the integrity of the header. Next, it unblinds the routing information to determine the next downstream node and removes one layer of encryption from the encrypted payload. At this point, the node is able to decide whether it is the final recipient of the message or it is supposed to forward the packet to the next hop.

\begin{comment}
\paragraph{Notation:}Let $\kappa=128$ be the security parameter. With non-negligible probability, an adversary must perform around $2^\kappa$ operations to break the security of Sphinx.

Let $r$ be the maximum number of nodes that a Sphinx mix message will traverse before being delivered to its destination.

$G$ is a prime order cyclic group satisfying the decisional Diffie-Hellman assumption \cite{Boneh_1998}. We use the secp256k1 elliptic curve \cite{secp}. The element $g$ is a generator of $G$ and $q$ is the (prime) order of $G$, with $q\approx2^{2*\kappa}$.

$G^*$ is the set of non-identity elements of G. $h_b$ is a pre-image resistant hash function used to compute blinding factors and modelled as a random oracle such that
$h_b:G^*\times G^*\rightarrow\mathbb{Z}^*_q$, where $\mathbb{Z}^*_q$ is the field of non-identity elements of $\mathbb{Z}_q$ (field of integers). We use the BLAKE2s hash function \cite{blake2}.

Each node $i$ has a private key $x_{i}\in \mathbb{Z}^*_q$ and a public key $y_{i}=g^{x_{i}}\in G^*$.
$\alpha_i$ is the group elements which, when combined with the nodes’ public keys, allow a shared key to be computed for each via Diffie-Hellman (DH) key exchange. This ensures that each node in the user-chosen route can forward the packet to the next, and only the receiving mix node can decrypt it.
$s_i$ are the DH shared secrets, $b_i$ are the blinding factors.
\end{comment}

\input{sections/03-sphinx-packet-format/01-key-exchange.tex}
\input{sections/03-sphinx-packet-format/02-replay-protection.tex}
\input{sections/03-sphinx-packet-format/03-routing-information.tex}
\input{sections/03-sphinx-packet-format/04-shifting.tex}
\input{sections/03-sphinx-packet-format/05-integrity.tex}
\input{sections/03-sphinx-packet-format/06-payload-transformation.tex}
\input{sections/03-sphinx-packet-format/07-shorter-paths.tex}


\subsection{Implementation choices}

HOPR employs the following cryptographic primitives:

\begin{itemize}
    \item \textbf{Cyclic group} HOPR's Sphinx implementation uses an elliptic curve group on the secp256k1 curve. Operations are therefore performed on the elliptic curve.

    \item \textbf{Hash function} HOPR uses the BLAKE2s hash function, a cryptographic hash function faster than SHA-2 and SHA-3, yet at least as secure as SHA-3. It produces digests of 32 bytes.

    \item \textbf{MAC} HOPR uses HMAC based on the BLAKE2s hash function.

    \item \textbf{Encryption scheme} HOPR uses the LIONESS \cite{lionesspaper} implementation, using BLAKE2s as a hash function and ChaCha20 as a stream cipher.

    \item \textbf{Padding} The original Sphinx paper uses a sequence of 0s for padding. However, this allows the last mix node in the path to infer information about the length of the path and the final destination, hence breaking one of the security properties promised by Sphinx. In order to prevent this attack, HOPR replaces the 0-padding with randomized padding for the final mix node when $v<r$. This ensures the exit node cannot identify where the padding starts and thus will not be able to determine the path length. In the case where $v=r$ there is no need to add padding as the length of the path is the maximum length, and thus no additional information is being revealed.

\end{itemize}
