\subsection{Heartbeat}
HOPR nodes use a heartbeat mechanism to estimate the availability of nodes in the network. Nodes keep scores for each other that measure their health. They use a exponential backoff to efficiently measure health scores.

\subsubsection{Health Score}
Each node keeps a score of all other nodes it is aware of. A node increases another node's score if the latter node has been observed online and decreases if it the latter node cannot be reached. Each node that has a funded outgoing payment channel is initially listed with $healthScore = 0.2$. Responding to a \textit{ping} with a \textit{pong} packet or sending its own \textit{ping} increases a node's score by 0.1. Not responding to a \textit{ping} reduces a node's score by 0.1. The minimal node score is 0 and the maximal score is 1. Nodes with a $healthScore \ge healthThreshold$ are considered online and suitable for use in paths; nodes with lower scores are omitted. The default $healthThreshold$ is $0.5$.

\subsubsection{Exponential Backoff}
Since the network status can change abruptly, e.g., due to electricity outages or unstable network links, availability needs to be remeasured frequently. However, it is inefficient to constantly probe nodes that are known to be offline. To provide a dynamic trade-off for both cases, HOPR utilizes a heartbeat with exponential backoff. The time until the next \textit{ping} will be sent to a node increases with the number of failed ping attempts, $n_{fail}$, since the last successful attempt or the network start. A successful response to \textit{ping} resets the backoff timer.

$$ t_{bo} = {t_{base}}^{{f_{bo}}^{n_{fail}}} $$

where $t_{bo}$ is the backoff time, $t_{base} = 2s$ is the initial backoff time and $f_{bo} = 1.5$.

The maximal backoff time of 512 seconds corresponds to $n_{fail} = 5$.