\section{On-chain Commitment}

\subsection*{Definition}
A commitment scheme is a protocol between usually two parties $A$ and $B$ and fulfills two properties (hiding and biding).
\\~\\\textbf{Hiding:} The ability to commit a value only known by the sender.
\\~\textbf{Binding:} The committed value must be the only one that the sender can compute and that validates during the reveal phase. 
\\~\\HOPR uses on-chain commitments to verify whether a ticket is a win or not in order to redeem it later on. The relayer doesn't know beforehand whether the ticket is a win or not until they receive an acknowledgment from the next downstream node eand can't change the outcome.
\subsection{Setup phase}
Once a node joins the HOPR network, it creates an iterated commitment and stores the opening key in the database. 
Iterated commitment scheme means $open_n$ opens $cm_n$ whereas $open_{n-1}$ opens $cm_{n-1}=open_n$ and so on. 
\newline The final commitment is computed as $cm_n:= hash^n(r)$ where hash is a preimage-resistant hash function and 
$r$ is chosen uniformly at random by the node in order to prevent the issuer from knowing whether the ticket will be a win or not. 
\\~\\ Furthermore, it will prevent it from tweaking the given challenge such that the ticket cannot be a win.
The number of iterations $n$ can be chosen as a constant and should reflect the number of tickets a node intends to redeem.

\subsection{Opening phase}
In order to redeem a ticket, a node has to reveal the opening to the current commitment $cm_n$ that is stored in the smart contract. 
\\~The opening shouldn’t be revealed otherwise since it discloses whether a ticket is a win or not.
The ticket is a win if: $$H( ticketHash, response, open ) <P_w$$ where $$ticketHash:=H(T_D)$$
The opening is computed as $open_{n-1} = hash^{n-1}(r)$ such that $cm_n=hash( open_{n-1})$. 
\\~\\The on-chain logic verifies whether the latest opening $open_n$ indeed opens the current on-chain commitment $cm_n$. 
If this is the case, the current on-chain commitment is replaced by the given opening. 
\\~The on-chain keeps track of updates to the on-chain commitments to prevent double-spending. 
So whenever a node resets a commitment, a counter, namely $account.counter$ is increased and a call to $updateCommitment$ invalidates all previously unredeemed tickets.








